Exploring the role of electric field in the catalase active site

### 2018-03-06 bb494/manuscript.tex
Add pymol sessions

\begin{figure}
  \caption{Depiction of catalase active pocket. \textbf{Left:} wildtype pocket with proposed ligand-orienting E-field \cite{electricpotential}. The field should orient H2O2 for optimal reaction with the heme. \textbf{Right:} modified HPII-3NY with a deprotonated 3-nitrotyrosine residue at site 206, with hypothetical augmented E-field. The disrupted E-field should result in un- or mis-aligned substrate.}
  \label{fig:hypothesis}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.29\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
  \begin{minipage}{.9\textwidth}
    \begin{tabular}{lll}
      \hline
      Sample  & $K_M$ (M) & kcat ($s^{-1}$) \\
      \hline
      HPII        & $1.3$ & $2.3x10^6$\\
      HPII-3NY    & $1.4$ & $6.9x10^6$\\
      HPII-pAzF   & $1.7$ & $2.2x10^5$\\
      \hline
    \end{tabular}
  \end{minipage}
  \end{subfigure}
  \begin{subfigure}{0.69\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
  \begin{minipage}{.9\textwidth}
    \includegraphics[width=\linewidth]{figures/fake-results.png}
  \end{minipage}
  \end{subfigure}
  \caption{Initial kinetic assay results. \textbf{a.} Final kinetic data extrapolated from Michaelis-Menten plot via linear regression. \textbf{b.} Michaelis-Menten plot of enzyme catalytic ($\pm \sigma^2$).}
  \label{fig:bradford-assay}
\end{figure}

@@

>>>>

\begin{figure}
  \begin{subfigure}{0.69\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{.9\textwidth}
      \includegraphics[width=0.5\linewidth]{figures/cartoon-visualization.png}%
      \includegraphics[width=0.5\linewidth]{figures/channel-visualization.png}
    \end{minipage}
  \end{subfigure}
  \begin{subfigure}{0.3\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
    \begin{minipage}{.9\textwidth}
      \includegraphics[width=\linewidth]{figures/active-site-visualization.png}%
    \end{minipage}
  \end{subfigure}

  \caption{Depiction of catalase active pocket. \textbf{Left:} wildtype pocket with proposed ligand-orienting E-field \cite{electricpotential}. The field should orient H2O2 for optimal reaction with the heme. \textbf{Right:} modified HPII-3NY with a deprotonated 3-nitrotyrosine residue at site 206, with hypothetical augmented E-field. The disrupted E-field should result in un- or mis-aligned substrate.}
  \label{fig:hypothesis}
\end{figure}

@@

\begin{figure}[h!]
  \centering
  \begin{subfigure}{0.29\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
  \begin{minipage}{.9\textwidth}
    \begin{tabular}{lll}
      \hline
      Sample  & $K_M$ (M) & kcat ($s^{-1}$) \\
      \hline
      HPII        & $1.3$ & $2.3x10^6$\\
      HPII-3NY    & $1.4$ & $6.9x10^6$\\
      HPII-pAzF   & $1.7$ & $2.2x10^5$\\
      \hline
    \end{tabular}
  \end{minipage}
  \end{subfigure}
  \begin{subfigure}{0.69\textwidth}
    \begin{minipage}{0.1\textwidth}\caption{}\end{minipage}%
  \begin{minipage}{.9\textwidth}
    %% \includegraphics[width=\linewidth]{figures/fake-results.png}
  \end{minipage}
  \end{subfigure}
  \caption{Initial kinetic assay results. \textbf{a.} Final kinetic data extrapolated from Michaelis-Menten plot via linear regression. \textbf{b.} Michaelis-Menten plot of enzyme catalytic ($\pm \sigma^2$).}
  \label{fig:bradford-assay}
\end{figure}

@@

new stuff
---------------------------
Structure of Catalase HPII From Escherichia coli, at 1.9 A˚ Resolution, Bravo + Fita
Describes the channels in HPII
``Channels might be long and narrow to promote the selectivity for H2O2 of HPII''

--Find a way to get the 2 channels: main one (intake? distal?), 590-595 one (lateral?)
